The Impact of Alternation

### 2017-05-15 draft.tex
ok

xxx

@@

\section{Proofs}

>>>>

We have implemented both Algorithm \ref{alg:predabs} and
\ref{alg:impact} in a prototype tool\footnote{\url{XXXX}} that uses
the Z3 SMT solver\footnote{\url{https://github.com/Z3Prover/z3}} to
check satisfiability queries and generate interpolants in the theory
of linear integer arithmetic variables (LIA). We compared both
algorithms with a previous implementation of trace inclusion
procedure, called
\textsc{Includer}\footnote{\url{http://www.fit.vutbr.cz/research/groups/verifit/tools/includer/}},
that uses on-the-fly determinisation and lazy predicate abstraction
with interpolant-based refinement \cite{Tacas16}.

The results of the experiments are given in Table
\ref{tab:experiments}. We applied the tool on several array logic
entailments, which occur as verification conditions for imperative
programs with arrays \cite{cav09} (Array shift, Array rotation 1+2,
Array split) available online \cite{ntslib}. Then, we applied it on
proving safety properties of hardware circuits (HW Counter 1+2)
\cite{smrcka}. Finally, we considered two timed communication
protocols, consisting of systems that are asynchronous compositions of
timed automata, whom correctness specification are given by timed
automata monitors: two versions (correct and faulty) of the timed
Alternating Bit Protocol \cite{abp} and a~controller of a railroad
crossing \cite{henzinger:RealTimeSystems}. All results were obtained
on an XXXX CPU @ YYYY GHz machine with ZZZZ GB of RAM. Execution times
are given in seconds.

\begin{table}[htb]
\begin{center}
{\fontsize{8}{9}\selectfont
\begin{tabular}{||l|c|c|c|c|c||}
\hline
Example & $\len{\A}$ & $L(\A)=\emptyset$ ? & Algorithm \ref{alg:predabs} & Algorithm \ref{alg:impact} & \textsc{Includer} \\
\hline 
\hline
\end{tabular}
}
\caption{}\label{tab:experiments}
\end{center}
\end{table}

@@
